Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
fixing some older edit

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.   Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
\end{thm}

@@

\begin{defn}
Given a set $\La$ of \define{labels}, an \define{$\La$-graph} is a graph $s,t\maps E\to N$
 equipped with a function $\ell \maps E \to \La$.
 A \define{morphism} from the $\La$-graph 
 \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
 to the $\La$-graph 
\[ \xymatrix{\La & E' \ar@<2.5pt>[r]^{s'} \ar@<-2.5pt>[r]_{t'} \ar[l]_{\ell'} & N'} \]
is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$E$};
\node (A') at (0,-1) {$E'$};
\node (B) at (1,0) {$N$};
\node (B') at (1,-1) {$N'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$s$} (B)
(A') edge node[above]{$s'$} (B')
(A) edge node[left]{$f$} (A')
(B) edge node[right]{$g$} (B');

@@

When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
but following previous work \cite{BCR} we call an open $\La$-graph an \define{$\La$-circuit}.

There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
any set to the $\La$-graph with that set of nodes and no edges.  Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.  Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
\begin{itemize}
\item an object is a finite set,
\item a morphism is an isomorphism class of $\La$-circuits, where an
\define{$\La$-circuit} is a cospan in $\Graph_\La$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(S)$};
\node (B) at (1,0) {$G$};
\node (C) at (2,0) {$L(T)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above,left]{$$} (B)
(C)edge node[above]{$$}(B);
\end{tikzpicture}
\]
and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,-0.5) {$L(S)$};
\node (F) at (5,-0.5) {$L(T)$};
\node (G) at (4,0) {$G$};
\node (G') at (4,-1) {$G'$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o$} (G)
(G) edge node[left]{$h$} (G')
(E) edge node[above]{$i$} (G)
(E) edge node[below]{$i'$} (G')
(F) edge node[below]{$o'$} (G');
\end{tikzpicture}
\]
where $h$ is an isomorphism.
\end{itemize} 
This category has a nice universal property, found by Rosebrugh, Sabadini and
Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
% Replaced strict symmetric with symmetric strict three times below
Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
numbers, with tensor product of objects given by addition.  An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.   A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.

@@

\subsection{Double categories}\label{sec:doublecats}

>>>>

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor. Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

\begin{defn}
Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
 equipped with a function $\ell \maps E \to \La$.
 A \define{morphism} from the $\La$-graph 
 \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
 to the $\La$-graph 
\[ \xymatrix{\La & E' \ar@<2.5pt>[r]^{s'} \ar@<-2.5pt>[r]_{t'} \ar[l]_{\ell'} & N'} \]
is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$E$};
\node (A') at (0,-1) {$E'$};
\node (B) at (1,0) {$N$};
\node (B') at (1,-1) {$N'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$s$} (B)
(A') edge node[above]{$s'$} (B')
(A) edge node[left]{$f$} (A')
(B) edge node[right]{$g$} (B');

@@

When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.

There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
any set to the $\La$-graph with that set of nodes and no edges.  Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.  Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
\begin{itemize}
\item an object is a finite set,
\item a morphism is an isomorphism class of $\La$-circuits, where an
$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(S)$};
\node (B) at (1,0) {$G$};
\node (C) at (2,0) {$L(T)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above,left]{$$} (B)
(C)edge node[above]{$$}(B);
\end{tikzpicture}
\]
and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,-0.5) {$L(S)$};
\node (F) at (5,-0.5) {$L(T)$};
\node (G) at (4,0) {$G$};
\node (G') at (4,-1) {$G'$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o$} (G)
(G) edge node[left]{$h$} (G')
(E) edge node[above]{$i$} (G)
(E) edge node[below]{$i'$} (G')
(F) edge node[below]{$o'$} (G');
\end{tikzpicture}
\]
where $h$ is an isomorphism.
\end{itemize} 
This category has a nice universal property, found by Rosebrugh, Sabadini and
Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
% Replaced strict symmetric with symmetric strict three times below
Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
numbers, with tensor product of objects given by addition.  An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.   A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.

@@

\subsection{Double categories}\label{sec:doublecats}
%!!! Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
